Notebook of learning from ensemble labels

### 2021-08-17 docs/notebook_learn_dl_ensemble.Rmd
Some updates due to former changes

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
```

@@

```
scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
```

```
python hrlcm/fit_step_lr.py --exp_name unet_one_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_2.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_two_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
```

>>>>

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_only_clr_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
```

@@

```
scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
```

```
mv results/north/dl_catalog_train.csv results/north/dl_catalog_train_full.csv; mv results/north/dl_catalog_train_1.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_one_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_2.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_two_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
```
